PhD Defense

### 2023-05-30 presentation/phd_defense_pres.tex
Add pictures souces

\uncover<2->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{orange}{First-Principle Models:}
\begin{itemize}
	\item Require extensive knowledge of the phenomenon
	\item Require a lot of compute for simulating large-scale phenomena
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{Figures/NN.jpg}
\end{columns}
}
\vspace{2em}
\uncover<3->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{green}{Data-Driven Models:}
\begin{itemize}
	\item Require a lot of data
	\item Often struggle to extrapolate
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.8\textwidth]{Figures/nn_schematics.pdf}
\end{columns}
}
\vspace{2em}
\uncover<4->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{blue}{Hybrid Models: }
\begin{itemize}
	\item Incorporate elements of both approaches
	\item Supplement data with knowledge or priors
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.7\textwidth]{Figures/NS_pic.png}
\end{columns}
}
\end{frame}

@@

\begin{frame}{Discussion and Limitations}
We showed that:
\begin{itemize}
	\item Physics-informed loss improves accuracy and forecasting stability of ROMs
	\item Collocations can supplement data to improve model's performance for unseen initial conditions.
\end{itemize}
\vspace{2em}
Limitations:
\begin{itemize}
	\item Optimal choice of collocations is problem-specific
	\item Need a lot of collocations
	\begin{itemize}
		\item \textit{Could} be possible to overcome with smarter sampling techniques
	\end{itemize}
\end{itemize}
\end{frame}

>>>>

\uncover<2->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{orange}{First-Principle Models}
\begin{itemize}
	\item Require extensive knowledge of the phenomenon
	\item Require a lot of compute for simulating large-scale phenomena
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{Figures/NN.jpg}
\end{columns}
}
\vspace{2em}
\uncover<3->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{green}{Data-Driven Models}
\begin{itemize}
	\item Require a lot of data
	\item Often struggle to extrapolate
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.8\textwidth]{Figures/nn_schematics.pdf}
\end{columns}
}
\vspace{2em}
\uncover<4->{
\begin{columns}[T,onlytextwidth]
\column{0.6\textwidth}
\textcolor{blue}{Hybrid Models}
\begin{itemize}
	\item Incorporate elements of both approaches
	\item Supplement data with knowledge or priors
\end{itemize}
\column{0.4\textwidth}
\centering
\includegraphics[width=0.5\textwidth]{Figures/NS_pic.png}
\end{columns}

Pictures sources: \footnote{\href{https://en.wikipedia.org/wiki/Navier–Stokes_equations}{Wikipedia: Navier-Stokes}},\footnote{\href{https://www.tibco.com/reference-center/what-is-a-neural-network}{tibco.com}},\footnote{\href{https://www.comsol.com/model/water-purification-reactor-14049}{COMSOL Simulations}}
}
\end{frame}

@@

\begin{frame}{Discussion and Limitations}
We showed that:
\begin{itemize}
	\item Physics-informed loss improves accuracy and forecasting stability of ROMs
	\item Collocations can supplement data to improve model's performance for unseen initial conditions.
\end{itemize}
\vspace{2em}
Limitations:
\begin{itemize}
	\item Optimal choice of collocations is problem-specific
	\item Need a lot of collocations
	\begin{itemize}
		\item \textit{Seems} possible to overcome with smarter sampling techniques
	\end{itemize}
\end{itemize}
\end{frame}
